The Globular Cluster System of the Auriga Simulations

### 2019-03-26 AurigaGCS.tex
R of radius wrapped in LaTeX math

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
        range of the colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-R$_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
        range of the colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}
